Equation-of-state insensitive relations after GW170817

### 2019-02-20 paper/bin-love-after-gw170817.tex

Now that we have obtained the residuals on $\Lambda_a$, we must convert them into residuals on the new tidal parameter $\lambda_0$, in order to compute and easily compare the systematic uncertainties to the statistical uncertainties on $\lambda_0$. {\ny{You need to say explicitly how you did this.}}
Figure~\ref{fig:qLsResiduals} shows the standard deviations of these residuals (converted into $\lambda_0$) binned in both $q$ and $\Lambda_s$. 
To estimate the overall systematic uncertainties on $\lambda_0$ accrued upon the use of the improved binary Love relations, we combine the uncertainties in both $q$ and $\Lambda_s$.
Figure~\ref{fig:residuals} displays the un-binned Gaussian distribution of $\lambda_0$ residuals for both the constrained, and unconstrained sets of EoSs for comparison.
Observe how the standard deviations $\sigma=9.764$ and $\sigma=78.28$ show a large decrease from the unconstrained to the constrained sets of EoSs.
Additionally, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=13.19$, $P_{99}=42.38$, and $P_{100}=111.32$ for the constrained EoSs.
Because the un-binned residuals seen in Fig.~\ref{fig:residuals} are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$) shown by Fig.~\ref{fig:qLsResiduals}, we consider the 90th percentile uncertainty (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals}) for the remainder of the analysis, in order to further take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$).
We take this value of $P_{90}=13.19$ to be the systematic measurement uncertainty introduced by using the improved binary Love relations on the parameter extraction of $\lambda_0$, indicated by the dashed indigo line in Fig.~\ref{fig:stackedFisher}.
Similarly, we derive the systematic measurement uncertainty on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
Currently, the statistical uncertainty of $170.1$ on $\lambda_0$ from GW170817 dominates the error budget compared to the systematic uncertainty of $13.19$, as seen in Fig.~\ref{fig:stackedFisher}.
This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
However, future detectors (for example aLIGO at design sensitivity, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical uncertainties and allowing for larger binary NS merger detection rates; further reducing the statistical uncertainties.
In Sec.~\ref{sec:futureObservations}, we analyze this further and discuss when the systematic uncertainties from EoS-insensitive relations become comparable to the statistical uncertainties.

>>>>

Finally, in order to marginalize over such errors, one would compute $\Lambda_a$ given selected values of $q$ and $\Lambda_s$ like so:
\begin{equation}
\Lambda_a=\Lambda_a^{\text{relation}}(\Lambda_s,q)+\mathcal{N}(\mu(\Lambda_s,q),\sigma(\Lambda_s,q)),
\end{equation}
where $\mathcal{N}(\mu,\sigma)$ is a normal distribution with mean and variance $\mu$ and $\sigma^2$.

However, for the extent of this analysis we are interested in obtaining an estimate for the amount of systematic uncertainties in $\lambda_0$ accrued upon the use of the improved binary Love relations. 
Such an approximation would allow us to compare the systematic and statistical uncertaintes in order to determine when the former will dominate the latter.
Similar to what was previously done, we sample $q$ and $\Lambda_s$ in order compute the residuals from the binary Love fits in $\lambda_0$ as $\lambda_0^{\text{relation}}(\Lambda_s,q)-\lambda_0^{\text{true}}$.
Figure~\ref{fig:residuals} displays the probability distribution of such $\lambda_0$ residuals (for both the constrained and unconstrained EoSs for comparison), which is observed to approximately obey a Gaussian distribution, as assumed.
Observe how the standard deviations $\sigma=9.764$ and $\sigma=78.28$ show a large decrease from the unconstrained to the constrained sets of EoSs.
Additionally, we find the 90th, 99th, and 100th percentiles on $\lambda_0$ to be $P_{90}=13.19$, $P_{99}=42.38$, and $P_{100}=111.32$ for the constrained EoSs.

For demonstration purposes, Fig.~\ref{fig:qLsResiduals} displays the standard deviations of $\lambda_0$ residuals binned in $q$ and $\Lambda_s$, as was done previously for $\Lambda_s$ residuals.
Observe how the uncertainties in $\lambda_0$ are dominated by the low-error regions of the parameter space ($\Lambda_s \rightarrow 0$, $\Lambda_s \rightarrow \infty$, $q \rightarrow 0$ and $q \rightarrow 1$).
in order to take into account the high-error regions of the parameter space ($\Lambda_s \sim 2000$, $q\sim0.5$), we conservatively approximate the systematic error in the binary Love relations to be the 90th percentile uncertainty $P_{90}=13.19$ (indicated by the dashed green line in Fig.~\ref{fig:qLsResiduals} and the dashed indigo line in Fig.~\ref{fig:stackedFisher}) for the remainder of the analysis.
Similarly, we derive the systematic measurement uncertainty on $\tilde\Lambda$ to be $12.01$, shown in Fig.~\ref{fig:singleFisherLt}.
Currently, the statistical uncertainty of $170.1$ on $\lambda_0$ from GW170817 dominates the error budget compared to the systematic uncertainty of $13.19$, as seen in Fig.~\ref{fig:stackedFisher}.
This means that, for the current ``O2" detector sensitivity, the use of improved binary Love relations will only make a negligible difference on the extraction of $\tilde\Lambda$.
However, future detectors (for example aLIGO at design sensitivity, A\texttt{+}, Voyager, CE, and ET) are planned with large reductions in sensitivity - both decreasing the statistical uncertainties and allowing for larger binary NS merger detection rates; further reducing the statistical uncertainties.
In Sec.~\ref{sec:futureObservations}, we analyze this further and discuss when the systematic uncertainties from EoS-insensitive relations become comparable to the statistical uncertainties.
